---
title: "Lab6_report"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab6_report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab6)
```


#Description

The package Lab6 includes the following implementations of the knapsack problem solution: Brute force ,dynamic and greedy heuristic.


```{r}
library(Lab6)
library(parallel)
```

#Data

```{r}
RNGversion(min(as.character(getRversion()),"3.5.3"))

set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
```

#Brute force

```{r}
brute_force_knapsack(x = knapsack_objects[1:8, ], W = 3500)
brute_force_knapsack(x = knapsack_objects[1:12, ], W = 3500)
brute_force_knapsack(x = knapsack_objects[1:8, ], W = 2000)
brute_force_knapsack(x = knapsack_objects[1:12, ], W = 2000)
```

How much time does it take to run the algorithm for n=16 objects?

```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W =3500))
```


It took 0.04 sec to run the algorithm for 16 objects.


#Dynamic

```{r}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
knapsack_dynamic(x = knapsack_objects[1:12,], W = 3500)
knapsack_dynamic(x = knapsack_objects[1:8,], W = 2000)
knapsack_dynamic(x = knapsack_objects[1:12,], W = 2000)
```



How much time does it take to run the algorithm for n = 500 objects?


```{r}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W =3500))
```

It took 2.14 sec to run the algorithm for 500 objects.


#Greedy heuristic

```{r}
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
greedy_knapsack(x = knapsack_objects[1:1200,], W = 2000)
```

How much time does it take to run the algorithm for n = 1000000 objects?


```{r}
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W =3500))
```


It took 0.72 sec to run the algorithm for 1000000 objects.


#Parallelizing brute force

What performance gain could you get by parallelizing brute force search?


```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500))
```

```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500, parallel = TRUE))
```







