---
title: "Lab6_report"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab6_report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab6)
```


#Description

The package Lab6 includes the following implementations of the knapsack problem solution: Brute force ,dynamic and greedy heuristic.


```{r}
library(Lab6)
library(parallel)
```

#Data

```{r}
RNGversion(min(as.character(getRversion()),"3.5.3"))

set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
```

#Brute force

```{r}
brute_force_knapsack(x = knapsack_objects[1:8, ], W = 3500)
brute_force_knapsack(x = knapsack_objects[1:12, ], W = 3500)
brute_force_knapsack(x = knapsack_objects[1:8, ], W = 2000)
brute_force_knapsack(x = knapsack_objects[1:12, ], W = 2000)
```

How much time does it take to run the algorithm for n=16 objects?

```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W =3500))
```


It took 2.47 sec to run the algorithm for 16 objects.


#Dynamic

```{r}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
knapsack_dynamic(x = knapsack_objects[1:12,], W = 3500)
knapsack_dynamic(x = knapsack_objects[1:8,], W = 2000)
knapsack_dynamic(x = knapsack_objects[1:12,], W = 2000)
```



How much time does it take to run the algorithm for n = 500 objects?


```{r}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W =3500))
```

It took 2.11 sec to run the algorithm for 500 objects.


#Greedy heuristic

```{r}
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
greedy_knapsack(x = knapsack_objects[1:1200,], W = 2000)
```

How much time does it take to run the algorithm for n = 1000000 objects?


```{r}
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W =3500))
```


It took 0.96 sec to run the algorithm for 1000000 objects.


#Parallelizing brute force

What performance gain could you get by parallelizing brute force search?


```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500))
```

```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500, parallel = TRUE))
```

It took 0.03 sec to run the algorithm for 8 objects and 0.02 to run the algorithm for 8 objects using the parallel method.
Speedup = 0.03 seconds / 0.02 seconds = 1.5 
By parallelizing the brute force for the knapsack problem with 8 objects, we achieved a speedup of 1.5, which means the parallel version is 1.5 times faster than the non-parallel version.




#Profiling the code with parallel method

If parallel TRUE:

temp_dfs <- parallel::mclapply(combinations, function(y) {
      selected_items <- x[as.logical(y), ]
      list(value = sum(selected_items$v), weight = sum(selected_items$w))
    })
    values <- sapply(temp_dfs, function(x) x$value)
    weights <- sapply(temp_dfs, function(x) x$weight)




If parallel FALSE:

for (i in counter) {
      selected_items <- x[as.logical(combinations[[i]]), ]
      values[i] <- sum(selected_items$v)
      weights[i] <- sum(selected_items$w)
    }



It took 0.03 sec to run the algorithm for 8 objects and 0.02 to run the algorithm for 8 objects using the parallel method.
Speedup = 0.03 seconds / 0.02 seconds = 1.5 
By parallelizing the brute force for the knapsack problem with 8 objects, we achieved a speedup of 1.5, which means the parallel version is 1.5 times faster than the non-parallel version.






